### 2016-09-30 supplement.tex
Fix supplement intro for SymPy Gamma
Add color to the links in the paper and supplement
What do people think? We can remove this if people don't like it. I wanted to
add it because some things that were links were subtle, and probably wouldn't
be noticed by most readers.
Unnecessary comma

\usepackage{amsmath}
\usepackage{url}
\usepackage{hyperref}

% this is required for all the \url{} commands in the bib file
%\usepackage{hyperref}

@@

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section~\ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections~\ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section~\ref{suppsec:numsimpl}
discusses numerical simplification.  Section~\ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In section
\ref{suppsec:sympy-gamma} the SymPy Gamma
and the SymPy Live projects are introduced.  Finally, section~\ref{suppsec:comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica.

>>>>

\usepackage{amsmath}
\usepackage{url}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  citecolor=black
}

@@

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section~\ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections~\ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section~\ref{suppsec:numsimpl}
discusses numerical simplification.  Section~\ref{suppsec:examples} provides
additional examples for topics discussed in the main paper.  In section
\ref{suppsec:sympy-gamma} the SymPy Gamma
project is discussed.  Finally, section~\ref{suppsec:comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica.
